---
title: "Tracking Cookies Data Analysis - ATT & Verizon"
author: "Alex Pinto / Kenn White"
date: "November 18, 2014"
output: html_document
---

Adding some libraries
```{r}
library(data.table)
library(lubridate)
library(reshape2)
library(ggplot2)
```

Setting up the path of the files we want to analyse
```{r}
logs_path = file.path(getwd(), "clean_logs")
apache_log_path = file.path(logs_path, "sniff_apache_log.txt")
trackertime_log_path = file.path(logs_path, "trackers_unix_times.txt")
```

Reading the apache_logs and doing some light regex. We will extract the date and the
user agent for further editing
```{r}
apache_logs = readLines(apache_log_path)
apache_len = length(apache_logs)
parsed_apache_ts = gsub("^\\[(.*?)\\] .*? (.*) /var/www/html/sniff.*", "\\1", apache_logs)
parsed_apache_agent = gsub("^\\[(.*?)\\] .*? (.*) /var/www/html/sniff.*", "\\2", apache_logs)
dt_apache = data.table(timestamp = parsed_apache_ts, agent = parsed_apache_agent)
rm(apache_logs, parsed_apache_ts, parsed_apache_agent)

## Only mobile (Android + iPhone) stuff, plz
## Oh, BTW, there is BlackBerry too
dt_apache = dt_apache[  grepl("Android", dt_apache$agent) 
                      | grepl("iPhone", dt_apache$agent)
                      | grepl("BlackBerry", dt_apache$agent)
                      | grepl("BB10", dt_apache$agent)]

print(paste("Percentage of traffic coming from Android and iPhone:", nrow(dt_apache)/apache_len))
print(head(dt_apache))
```

Reading the tracker logs and extracting the data from the timestamp and tracker data.
Separate them out for independent tracking
```{r}
trackertime_logs = readLines(trackertime_log_path)
print(length(trackertime_logs))
dt_tracker = as.data.table(matrix(unlist(strsplit(trackertime_logs, "\\|")), ncol=2, byrow=T))
setnames(dt_tracker, c("V1","V2"), c("tracker", "timestamp"))
dt_tracker[, timestamp := as.integer(as.character(timestamp))]

## Separating the tracker groups out
dt_att = dt_tracker[grepl("ACR", dt_tracker$tracker, fixed=TRUE)]
dt_verizon = dt_tracker[grepl("UIDH", dt_tracker$tracker, fixed=TRUE)]

print(nrow(dt_att))
print(dt_att)
print(nrow(dt_verizon))
print(dt_verizon)
```

Cleaning up the timestamps on the Apache logs and flooring the date for counting
how many entries we have on each day. Calulating the tables of entries per day.
```{r}
ts_apache = parse_date_time(dt_apache$timestamp, orders="%d/%b/%Y:%H:%M:%S %z", tz="UTC")
ts_apache_floor = floor_date(ts_apache, "day")
table_apache = table(ts_apache_floor)
table_apache
````

Cleaning up the timestamps on the ATT and Verizon data flooring the date for counting
how many entries we have on each day. Calculating the proportions

```{r}
ts_att = as.POSIXct(dt_att$timestamp, origin="1970-01-01", tz="UTC")
ts_att_floor = floor_date(ts_att, "day")
table_att = table(ts_att_floor)
print(table_att)
prop_att = table_att/table_apache
print(prop_att)
```

```{r}
ts_verizon = as.POSIXct(dt_verizon$timestamp, origin="1970-01-01", tz="UTC")
ts_verizon_floor = floor_date(ts_verizon, "day")
table_verizon = table(ts_verizon_floor)
print(table_verizon)
prop_verizon = table_verizon/table_apache
print(prop_verizon)
```

All right! Let's try to create a graph now!

```{r}
dt_graph = rbind(data.table(Date=names(prop_verizon), Percentage=as.numeric(prop_verizon), ISP="Verizon"),
                 data.table(Date=names(prop_att), Percentage=as.numeric(prop_att), ISP="AT&T"))

ggplot(dt_graph, aes(Date, Percentage, fill=ISP)) +
    geom_bar(position="dodge", stat="identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=10)) +
    theme(axis.text.y = element_text(hjust = 1, size=12)) +
    ggtitle("Percentage of Verizon and AT&T UIDs over time\nAs seen on lessonslearned.org/sniff")
```

We can do Stacked Bars as well!

```{r}
ggplot(dt_graph, aes(Date, Percentage, fill=ISP)) +
    geom_bar(stat="identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=10)) +
    theme(axis.text.y = element_text(hjust = 1, size=12)) +
    ggtitle("Percentage of Verizon and AT&T UIDs over time\nAs seen on lessonslearned.org/sniff")
```
